\bibitem[Atmel Corporation 2009]{avrdatasheet}
\abntrefinfo{Atmel Corporation}{ATMEL CORPORATION}{2009}
{ATMEL CORPORATION. \emph{8-bit AVR Microcontroller with 4/8/16/32K Bytes
  In-System Programmable Flash}.
San Jose, CA, 2009.}

\bibitem[Dargie e Poellabauer 2010]{dargie_poellabauer2010}
\abntrefinfo{Dargie e Poellabauer}{DARGIE; POELLABAUER}{2010}
{DARGIE, W.; POELLABAUER, C. \emph{Fundamentals of wireless sensor networks}.
  Chichester, West Sussex, U.K.: Wiley, 2010.}

\bibitem[Gadre 2001]{gadre2001}
\abntrefinfo{Gadre}{GADRE}{2001}
{GADRE, D.~V. \emph{Programming and customizing the AVR microcontroller}. New
  York: McGraw-Hill, 2001.}

\bibitem[Karl e Willig 2005]{karl_willig2005}
\abntrefinfo{Karl e Willig}{KARL; WILLIG}{2005}
{KARL, H.; WILLIG, A. \emph{Protocols and architectures for wireless sensor
  networks}. Hoboken, NJ: Wiley, 2005.}

\bibitem[L\'opez e Zhou 2008]{lopez_zhou2008}
\abntrefinfo{L\'opez e Zhou}{L\'OPEZ; ZHOU}{2008}
{L\'OPEZ, J.; ZHOU, J. \emph{Wireless sensor network security}. Amsterdam: IOS
  Press, 2008.}

\bibitem[Nordic Semiconductor 2008]{nrfdatasheet}
\abntrefinfo{Nordic Semiconductor}{NORDIC SEMICONDUCTOR}{2008}
{NORDIC SEMICONDUCTOR. \emph{nRF24L01+: Single Chip 2.4GHz Transceiver -
  Product Specification v1.0}.
Trondheim, 2008.}

\bibitem[Trevennor 2012]{trevennor2012}
\abntrefinfo{Trevennor}{TREVENNOR}{2012}
{TREVENNOR, A. \emph{Practical AVR microcontrollers}. Berkeley, CA: Apress,
  2012.}

\bibitem[Williams 2014]{williams2014}
\abntrefinfo{Williams}{WILLIAMS}{2014}
{WILLIAMS, E. \emph{Make: AVR Programming}. Sebastopol, Calif.: Maker Media,
  2014.}

\bibitem[Aldrich 2003]{aldrich2003}
\abntrefinfo{Aldrich}{ALDRICH}{2003}
{ALDRICH, F.~K. Smart homes: Past, present and future. In:  HARPER, R. (Ed.).
  \emph{Inside the Smart Home}. London: Springer, 2003.}

\bibitem[Buratti 2011]{buratti2011}
\abntrefinfo{Buratti}{BURATTI}{2011}
{BURATTI, C. \emph{Sensor networks with IEEE 802.15.4 systems}. Berlin:
  Springer, 2011.}

\bibitem[Hagen 2002]{hagen2002}
\abntrefinfo{Hagen}{HAGEN}{2002}
{HAGEN, S. \emph{IPV6 essentials}. Beijing: O'Reilly, 2002.}

\bibitem[Harper 2003]{harper2003}
\abntrefinfo{Harper}{HARPER}{2003}
{HARPER, R. Inside the smart home: Ideas, possibilities and methods. In:
  HARPER, R. (Ed.). \emph{Inside the Smart Home}. London: Springer, 2003.}

\bibitem[Kuorilehto et al. 2007]{kuorilehto2007}
\abntrefinfo{Kuorilehto et al.}{KUORILEHTO et al.}{2007}
{KUORILEHTO, M. et al. \emph{Ultra-low energy wireless sensor networks in
  practice}. Chichester, England: John Wiley & Sons, 2007.}

\bibitem[Kyas 2013]{kyas2013}
\abntrefinfo{Kyas}{KYAS}{2013}
{KYAS, O. \emph{How To Smart Home}. Wyk, Germany: Key Concept Prees e.K.,
  2013.}

\bibitem[Riley 2012]{riley2012}
\abntrefinfo{Riley}{RILEY}{2012}
{RILEY, M. \emph{Programming your home}. Dallas, Tex.: Pragmatic Bookshelf,
  2012.}

\bibitem[Shelby e Bormann 2009]{shelby_bormann2009}
\abntrefinfo{Shelby e Bormann}{SHELBY; BORMANN}{2009}
{SHELBY, Z.; BORMANN, C. \emph{6LoWPAN: The Wireless Embedded Internet}.
  Chichester, U.K.: J. Wiley, 2009.}

\bibitem[Sohraby, Minoli e Znati 2007]{sohraby_minoli_znati2007}
\abntrefinfo{Sohraby, Minoli e Znati}{SOHRABY; MINOLI; ZNATI}{2007}
{SOHRABY, K.; MINOLI, D.; ZNATI, T.~F. \emph{Wireless sensor networks}.
  Hoboken, N.J.: Wiley-Interscience, 2007.}

\bibitem[Texas Instruments 2015]{ccdatasheet}
\abntrefinfo{Texas Instruments}{TEXAS INSTRUMENTS}{2015}
{TEXAS INSTRUMENTS. \emph{CC2500 - Low-Cost Low-Power 2.4 GHz RF Transceiver}.
Dallas, Texas, 2015.}


